Detecting AI-Generated Images using ResNet

### 2022-12-14 paper/paper.tex
Update paper

\begin{figure}[h]
  \centering
  \includegraphics[width=140pt]{./assets/paper_indoor_dataset.jpg}
  \caption{Indoor Scene Recognition Database Examples}
  \label{fig:paper_indoor_dataset}
\end{figure}

@@

The Weather Image Recognition Dataset contains labeled 6738 images of different types of weather, its catogories including dew, fog, frost, glaze, etc \cite{DVN/M8JQCR_2021}. This dataset is used in our experiment to evaluate our model's generalization ability and performance on other kinds of photos than indoors.

\begin{figure}[h]
  \centering
  \includegraphics[width=140pt]{./assets/paper_weather_dataset.jpg}
  \caption{Weather Image Recognition Dataset Examples}
  \label{fig:paper_weather_dataset}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=140pt]{./assets/paper_comic_dataset.jpg}
  \caption{Comic Books Images Dataset Examples}
  \label{fig:paper_comic_dataset}
\end{figure}

@@

By running CLIP-image-encoder-guided Stable Diffusion mentioned in Section \ref{sec:datasets_image_variation_generation} on our raw datasets, we built our main dataset from the indoor dataset in Section \ref{sec:indoor_dataset} which contains 15,621 real-world in-door photos and combined with another 15,621 generated images that are similar to the real-world photos. Aside from the main dataset, we also built two smaller datasets from the weather dataset in \ref{sec:weather_dataset} and the comic book dataset in \ref{sec:comic_dataset} for testing the model's generalization on other genres of photos. For each image in this dataset, we applied center-cropping and resizing postprocessing to make sure they are consistent in image size, being 256x256.

@@

ResNet, short for Residual Network, provides another way for data to reach later regions of the neural network by skipping some layers. Consider a series of layers, from layer $I$ to layer $I + n$, and the function $F$ that these layers represent. Layer $i$'s input is denoted by $x$. $x$ will simply run through these layers one by one in a classic feedforward arrangement, and the result of layer $I + n$ is $F(x)$$.

@@

Experiment results go here.

\begin{figure}[htbp]
\centering
\subfigure{
\begin{minipage}[t]{\linewidth}
\centering
\includegraphics[width=4in]{paper/training_confusion_matrix.jpg}
\caption{Validation Confusion Matrix}
\end{minipage}%
}%
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=140pt]{./assets/paper_indoor_dataset.jpg}
  \caption{Indoor Scene Recognition Database Examples}
  \label{fig:paper_indoor_dataset}
\end{figure}

@@

The Weather Image Recognition Dataset contains labeled 6738 images of different types of weather, its catogories including dew, fog, frost, glaze, etc \cite{haixia2021weather}. This dataset is used in our experiment to evaluate our model's generalization ability and performance on other kinds of photos than indoors.

\begin{figure}[ht]
  \centering
  \includegraphics[width=140pt]{./assets/paper_weather_dataset.jpg}
  \caption{Weather Image Recognition Dataset Examples}
  \label{fig:paper_weather_dataset}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=140pt]{./assets/paper_comic_dataset.jpg}
  \caption{Comic Books Images Dataset Examples}
  \label{fig:paper_comic_dataset}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{./assets/paper_dataset_processed.jpg}
  \caption{Stable Diffusion Image-to-Image Examples}
  \label{fig:paper_processed_dataset}
\end{figure}

By running the text-conditioned CLIP-guided Stable Diffusion mentioned in Section \ref{sec:datasets_image_variation_generation} on our raw datasets, we built our main dataset from the indoor dataset in Section \ref{sec:indoor_dataset} which contains 15,621 real-world in-door photos and combined with another 15,621 generated images that are similar to the real-world photos. Two examples from this dataset are shown in Figure \ref{fig:paper_processed_dataset}. Aside from the main dataset, we also built two smaller datasets from the weather dataset in \ref{sec:weather_dataset} and the comic book dataset in \ref{sec:comic_dataset} for testing the model's generalization on other genres of photos. For each image in this dataset, we applied center-cropping and resizing postprocessing to make sure they are consistent in image size, being 256x256. Apart from that, we also utilized OpenAI's DALL·E 2's image variation generation API to generate two small datasets from a subset of the indoor dataset and the weather dataset, the former containing 625 AI-generated images + 625 real-world photos, and the latter containing 301+301 images.

@@

ResNet, short for Residual Network, provides another way for data to reach later regions of the neural network by skipping some layers. Consider a series of layers, from layer $I$ to layer $I + n$, and the function $F$ that these layers represent. Layer $i$'s input is denoted by $x$. $x$ will simply run through these layers one by one in a classic feedforward arrangement, and the result of layer $I + n$ is $F(x)$.

@@

% TODO: Placeholder for now, data not real
\begin{table*}
  \centering
  \begin{tabular}{c|c||c|c|c|c}
    \hline
    \textbf{Dataset} & \textbf{Model} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-Score} & \textbf{Accuracy} \\
    \hline
    Indoor + SD & ResNet34       & {71.88\%}          & {61.33\%}       & {66.19\%}      & {71.88\%}    \\
    Indoor + SD & ResNet50           & {93.75\%}          & {90.00\%}       & {91.84\%}      & {71.88\%}    \\
    Weather + SD & ResNet34  & {93.19\%}          & {91.33\%}       & {92.25\%}       & {71.88\%}   \\
    Weather + SD & ResNet50       & {92.00\%}          & {92.00\%}       & {92.00\%}      & {71.88\%}    \\
    Comic + SD & ResNet34 & {92.00\%}          & {92.00\%}       & {92.00\%}      & {71.88\%}    \\
    Comic + SD & ResNet50 & {92.00\%}          & {92.00\%}       & {92.00\%}      & {71.88\%}    \\
    Small Indoor + DALLE2 & ResNet34 & {92.67\%}          & {92.67\%}       & {92.67\%}      & {71.88\%}    \\
    Small Indoor + DALLE2 & ResNet50 & {92.67\%}          & {92.67\%}       & {92.67\%}      & {71.88\%}    \\
    Weather + DALLE2 & ResNet34 & {92.67\%}          & {92.67\%}       & {92.67\%}      & {71.88\%}    \\
    Weather + DALLE2 & ResNet50 & {92.67\%}          & {92.67\%}       & {92.67\%}      & {71.88\%}    \\
    \hline
  \end{tabular}
  \caption{Precision, Recall and F1-Score on the \% datasets}
  \label{tab:results-on-datasets}
\end{table*}
